The DAO Hack

### 2019-01-06 paper/paper.tex
added dao part

Ethereum is one type of cryptocurrency.
Its main difference to others like Bitcoin is that it can run a complex programming language called Solidity.
With Solidity, you can create loops, functions and recursion which then are run on the ethereum blockchain.
This has huge advantages as one can create powerful smart contracts and bind the payment to those.
Only with such a powerful language the DAO could be created. \cite{eth}

@@

>>>>

Ethereum is one type of cryptocurrency.
The cash is calles ether.
Its main difference to others like Bitcoin is that it can run a complex programming language called Solidity.
With Solidity, you can create loops, functions and recursion which then are run on the ethereum blockchain.
This has huge advantages as one can create powerful smart contracts and bind the payment to those.
Only with such a powerful language the DAO could be created. \cite{eth}

\subsection{Investment Fund}

An investment fund is a fund where investors can invest money.
With the money the fund manager manages which shares to buy/sell when based on the defined goals, risks and other factors of the specific fund.
The gain can then be payed out to the investors and the loss will shrink the fund.

@@

The DAO is an open source software written in Solidity build on the ethereum blockchain.

The DAO is like an investment fund running without any hierarchical management.
Investors (ethereum addresses) can exchange ether for DAO tokens (the DAOs currency) in the initial phase.

The initial phase defines some starting properties of the DAO like the minimum ether required to successfully build the DAO.
Instead of a fund manager like in the investment fund each investor gets voting rights based on the invested money.
With this voting rights one can vote where the money should be invested.
To propose an investment an investor can create a proposal.
The proposal contains the recipient (an ethereum address) of the investment, the amount in ether, the voting deadline, among other properties.
When a proposal is accepted, which means more than a given amount of votes voted yes the DAO executes the proposal, meaning it transfers the money to the recipient.
To prevent proposal spams the proposal creator has to pay a small fee for each proposal he creates, which he gets back iff the proposal is accepted.

But how do we prevent illegal proposals or proposals that pays out all the investment to a bad person who has more then 50\% of the voting rights?
For this reasons each DAO has the curator (an ethereum address), a person who can accept or reject proposals before the voting window gets opened.
This curator is also defined in the initial phase.

The curator principle removes a bit of the non hierarchical management.
To give the investors more flexibility they can change the curator at any time for any reason.
For this purpose one has to create a special proposal called a split proposal.
The creator defines a new curator in this proposal and the old curator can not reject it.
The DAO automatically starts the voting period.

After this period the DAO is split in two.
All investors voting yes are now in the new DAO and their investment is transfered to it while the others stay in the old one.
